---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# easylm

The goal of easylm is to provide a limited number of functions to analyze linear models.

-   lm_check() allow for a single function call to check linear models assumptions and to look for outliers.

-   lm_sum() allow for a single function call to give the usual anova statistics but also effect sizes and 95% confidence interval.

## Installation

You can install the development version of easylm like so:

``` r
devtools::install_github("ArthurDejean/easylm")
```

For the functions of this package to work, you need to install these fairly common packages in data analysis.

Here is a simple script to install them in your personal R environment :

``` r
packages = c("tidyverse", "knitr", "stats", "car", "lmtest", "tseries", "rsq", "broom", "gt", "patchwork")

for (element in packages) {
  if (require(element, character.only=T) == FALSE) {
    install.packages(element)
    require(element, character.only=T)
  } else {
    require(element, character.only=T)
  }
}

rm(packages,element)
```

## Example

This is a basic example of use of the two functions of this package

```{r example}
library(easylm)
M = lm(qsec~hp, mtcars)
lm_check(M)
#According to the Bonferroni test for outliers, Merc 230 is an outlier.

M = lm(qsec~hp, subset(mtcars, rownames(mtcars) != "Merc 230"))
lm_check(M) # we are going to ignore the independency of residuals issue for this example.

lm_sum(M)

#If you want to display this tab in a plot
lm_sum(M, plot = TRUE)

#If you want the predictors statistics only
lm_sum(M, plot = TRUE, type = "pred")
```
